An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-29 draft.tex
BBOB again
Update draft.tex

But this is a rule of thumb, and it will depend on the degree of heterogeneity,
as well as on the algorithm itself. Some level of heterogeneity can be
implemented by just changing the configuration parameters of each population,
but in this case, we are interested in a heterogeneous search strategy. 
Therefore, in this experiment we compare a multi-population with only GA and PSO populations,
versus an ensemble of GA and PSO algorithms. We tested on the first five functions of the
BOBB testbed. We used ten populations and eight workers for the experiment and the
same parameters as before.

@@

\begin{figure}[h!tb]
  % Is the axis correct? Seconds per instance or total time? Please
  % change that - JJ
    \centering
    \includegraphics[width=\textwidth]{sp_size_worker}
    \caption{Time required to complete experiments with different number of workers and populations sizes }
    \label{fig:spworker}
\end{figure}

>>>>

But this is a rule of thumb, and it will depend on the degree of heterogeneity,
as well as on the algorithm itself. Some level of heterogeneity can be
implemented by just changing the configuration parameters of each population,
but in this case, we are interested in a heterogeneous search strategy. 
Therefore, in this experiment we compare a multi-population with only GA and PSO populations,
versus an ensemble of GA and PSO algorithms. We tested on the first five functions of the
BBOB testbed. We used ten populations and eight workers for the experiment and the
same parameters as before.

@@

The

\begin{figure}[h!tb]
  % Is the axis correct? Seconds per instance or total time? Please
  % change that - JJ
  % Yes, they are instances - Mario
    \centering
    \includegraphics[width=\textwidth]{sp_size_worker}
    \caption{Time required, in seconds, to complete an instance of the function, with different number of workers and populations sizes }
    \label{fig:spworker}
\end{figure}
